---
title: "code highlight"
format: revealjs
editor: visual
---

## foo

```{r}
#| echo: TRUE
#| code-line-numbers: "3-13"

library(tidyverse)

my_emd <- c(
  "iletisim@ahmetbarut.net",
"akljd@mail.",
"askdioaj@gmail.com",
";lafjkl@duke.edu",
"ksdfhio@cs.duke.edu",
"afl;kl;d@gmail.com",
"kdijermkdf@gmail.com",
"kdifjfie@eenergy.com",
"whoa@hiduke.edu",
"joah@1duke.com")

my_df <- tibble(email = my_emd)
```

## Highlight

```{r}
#| echo: TRUE
#| code-line-numbers: "1|3,8,12-13"

my_emd <- c(
  "iletisim@ahmetbarut.net",
"akljd@mail.",
"askdioaj@gmail.com",
";lafjkl@duke.edu",
"ksdfhio@cs.duke.edu",
"afl;kl;d@gmail.com",
"kdijermkdf@gmail.com",
"kdifjfie@eenergy.com",
"whoa@hiduke.edu",
"joah@1duke.com")

my_df <- tibble(email = my_emd)
```

## box

::: {.two-column}

::: {.left-column}
This is the left column.
:::

::: {.right-column}
This is the right column.
:::

:::

<style>
.two-column {
  display: flex;
}

.left-column {
  flex: 1;
  background-color: #eee;
}

.right-column {
  flex: 1;
  background-color: #ccc;
}
</style>

## box layout

::: {layout="[[1,1], [1]]" style="background-color: grey;"}

the [color yellow background]{style="background-color: yellow;"}. is [red]{style="color: red; background-color: blue;"}

CAT

[SAT]{style="color: darkorange; background-color: yellow;"}
:::

## another

::: {layout="[ [1], [1,1] ]"}
This is column 1.

This is column 2.

with more text
:::

<!-- The following doesn't seem to work but comes from StackExchange -->
<style>
.quarto-column:nth-child(1) {
  background-color: #eee;
}

.quarto-column:nth-child(2) {
  background-color: #ccc;
}
</style>

## More boxes

::: {layout="[[70,30], [100]]"}

[Surus (surus.png) the second chilliest of the cools while wang Lin is considered only sub par when not contemplating nonsense]{style="background-color: cornflowerblue; background-clip: padding-box; border: none;"}

Hanno (hanno.png)

[Lin Wang (lin-wang.png) is the chilliest of the cools while wang Lin is considered only sub par when not contemplating nonsense]{style="background-color: #D3D3D3; border: none; padding: 10px; border-top: 1px solid #D3D3D3; border-bottom: 1px solid #D3D3D3;"}
:::

## more foo

[And now is the time for all good chat-poes to come to the aid of their coders]{style="background-color: #D3D3D3; border-radius: 10px; width: 50%;"}

## box layout

::: {layout="[[1,1], [1]]" style="background-color: grey;"}

the [color yellow background]{style="background-color: yellow;"}. is [red]{style="color: red; background-color: blue;"}

CAT

[SAT]{style="color: darkorange; background-color: yellow;"}
:::

::: {layout="[[1,1], [1]]" style="background-color: #D3D3D3; border-radius: 10px; width: 50%;"}

the [color yellow background]{style="background-color: red;"}. is [red]{style="color: yellow; background-color: blue;"}

CAT

[SAT]{style="color: darkorange; background-color: yellow;"}
:::

